Manuscript Template for a Data Analysis Project

### 2023-02-09 products/manuscript/MANU.qmd
used here package

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(tidyverse)
library(readxl)
library(lubridate)
library(stringr)
```

@@

```{r warning=FALSE}
setwd("../../")
his_deaths <- read_xlsx("data/raw_data/hivdeaths_his_1820.xlsx", skip = 1)
nhw_deaths <- read_xlsx("data/raw_data/hivdeaths_nhw_1820.xlsx", skip = 1)
nhb_deaths <- read_xlsx("data/raw_data/hivdeaths_nhb_1820.xlsx", skip = 1)

his_pop <- read_xlsx("data/raw_data/pop_his_1820.xlsx", skip = 1)
nhw_pop <- read_xlsx("data/raw_data/pop_nhw_1820.xlsx", skip = 1)
nhb_pop <- read_xlsx("data/raw_data/pop_nhb_1820.xlsx", skip = 1)
```

@@

```{r warning=FALSE}
setwd("../../")
sdoh <- read_xlsx("data/raw_data/AIDSVu_County_SDOH_2020.xlsx", skip = 3)
sdoh <- sdoh %>%  filter(State == "Georgia")

dx18 <- read_xlsx("data/raw_data/AIDSVu_County_NewDX_2018.xlsx", skip = 3)
dx18 <- dx18 %>%  filter(State == "Georgia") %>% 
  select(!contains(c("Rate Stability", "Percent", "Case")))

dx19 <- read_xlsx("data/raw_data/AIDSVu_County_NewDX_2019.xlsx", skip = 3)
dx19 <- dx19 %>%  filter(State == "Georgia")%>% 
  select(!contains(c("Rate Stability", "Percent", "Case")))

dx20 <- read_xlsx("data/raw_data/AIDSVu_County_NewDX_2020.xlsx", skip = 3)
dx20 <- dx20 %>%  filter(State == "Georgia") %>% 
  select(!contains(c("Rate Stability", "Percent", "Case")))
```

@@

```{r warning = false}
setwd("../../")
pov <- read_xlsx("data/raw_data/economics_22.xlsx", sheet = "poverty")

@@

Things are looking pretty good so frame, so let's save these dataframes.

```{r}
saveRDS(df, "../../data/df.rds")
saveRDS(dx, "../../data/dx.rds")
saveRDS(sdoh, "../../data/sdoh.rds")
saveRDS(pov, "../../data/pov.rds")
```

>>>>

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(tidyverse)
library(readxl)
library(lubridate)
library(stringr)
here::here()

@@

```{r warning=FALSE}
his_deaths <- read_xlsx(here("data/raw_data/hivdeaths_his_1820.xlsx"), skip = 1)
nhw_deaths <- read_xlsx(here("data/raw_data/hivdeaths_nhw_1820.xlsx"), skip = 1)
nhb_deaths <- read_xlsx(here("data/raw_data/hivdeaths_nhb_1820.xlsx"), skip = 1)

his_pop <- read_xlsx(here("data/raw_data/pop_his_1820.xlsx"), skip = 1)
nhw_pop <- read_xlsx(here("data/raw_data/pop_nhw_1820.xlsx"), skip = 1)
nhb_pop <- read_xlsx(here("data/raw_data/pop_nhb_1820.xlsx"), skip = 1)
```

@@

```{r warning=FALSE}
sdoh <- read_xlsx(here("data/raw_data/AIDSVu_County_SDOH_2020.xlsx"), skip = 3)
sdoh <- sdoh %>%  filter(State == "Georgia")

dx18 <- read_xlsx(here("data/raw_data/AIDSVu_County_NewDX_2018.xlsx"), skip = 3)
dx18 <- dx18 %>%  filter(State == "Georgia") %>% 
  select(!contains(c("Rate Stability", "Percent", "Case")))

dx19 <- read_xlsx(here("data/raw_data/AIDSVu_County_NewDX_2019.xlsx"), skip = 3)
dx19 <- dx19 %>%  filter(State == "Georgia")%>% 
  select(!contains(c("Rate Stability", "Percent", "Case")))

dx20 <- read_xlsx(here("data/raw_data/AIDSVu_County_NewDX_2020.xlsx"), skip = 3)
dx20 <- dx20 %>%  filter(State == "Georgia") %>% 
  select(!contains(c("Rate Stability", "Percent", "Case")))
```

@@

```{r warning = false}
setwd("../../")
pov <- read_xlsx(here("data/raw_data/economics_22.xlsx"), sheet = "poverty")

@@

Things are looking pretty good so far, so let's save these dataframes.

```{r}
saveRDS(df, here("data/processed_data/df.rds"))
saveRDS(dx, here("data/processed_data/dx.rds"))
saveRDS(sdoh, here("data/processed_data/sdoh.rds"))
saveRDS(pov, here("data/processed_data/pov.rds"))
```
